%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper]{moderncv}




% moderncv themes
%\moderncvtheme[gray]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

% character encoding

%\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins

\usepackage[scale=0.8]{geometry}
\usepackage{lastpage}
\rfoot{\addressfont\itshape\textcolor{black}{Page \thepage\ of \pageref{LastPage}}}

\firstname{Pavel}
\familyname{Aitkulov}
%\title{Resumé title (optional)}               % optional, remove the line if not wanted
%\address{Izhevsk}{Russia}    % optional, remove the line if not wanted
\mobile{+1-408-463-80-82}                    % optional, remove the line if not wanted
% \mobile{+7-909-052-31-13}                    % optional, remove the line if not wanted
\email{ajtkulov@gmail.com}                      % optional, remove the line if not wanted
\social[linkedin][https://www.linkedin.com/in/ajtkulov/]{linkedin.com/in/ajtkulov}


% \quote{Curriculum Vitae}                 

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\vspace{8pt}

$\circ$ Experienced Software Engineer with a strong track record solving business problems using advanced algorithms, machine learning, and functional programming

\vspace{2pt}

$\circ$ Proven ability to design and implement optimized data pipelines, perform data analysis, and deploy machine learning models in a production environment

\vspace{5pt}

\section{Education}
\cventry{2010}{Ph.D.}{Udmurt State University, Institute of Control Sciences V.A. Trapeznikov Academy of Sciences}{Izhevsk, Moscow}{Russia}{Key words: online string algorithms, string matching, text indexing, dynamic suffix arrays, data compression. Advisor: prof.~Nepejvoda~N.~N.} 
\cventry{2006}{MS in Computer Science}{Udmurt State University}{Izhevsk}{Russia}{Summa cum laude. 
Master thesis: Limited proof programming (Floyd-Hoare logic, annotated program, static verification, compiler)
}

\section{Skills}
\cvcomputer{Programming Languages}{Scala, Python, C\#, Java, compiler theory, functional programming, Effect system, ZIO}{Culture}{Tests, CI/CD, Code Reviews, Dashboards, Observability, Monitoring, Tech Lead for a team of 3}
\cvcomputer{Data}{Spark, Druid, Kafka, Pulsar, Cassandra, Big~Query, Akka, SQL, Clickhouse, Hive, Presto, Airflow, ETL, elastic, search index}{CS Interests}{graph theory, number theory, formal languages, string matching, data structures, domain-specific languages}
\cvcomputer{Infrastructure}{AWS, S3, EC2, LB, ECS, Docker, Spinnaker, k8s, Terraform}{ML}{LogReg, CatBoost/xgboost, NER, NLP, CV, ANN/KNN}

\section{Experience}
\cventry{07.2023--now}{Software/Data Engineer}{Disney Streaming, Santa Clara, CA}{}{}{
  AdTech, infrastructure, big data
  \begin{itemize}%
    \item Designed and implemented internal web applications to manage data pipelines and provide customer reports, 40-50Tb data per day, 11B events per day, 400+ clients.
  \end{itemize}
  Technologies: Scala, Java, Python, AWS, Airflow
}
\cventry{01.2020--04.2023}{ML Engineer}{Dun \& Bradstreet, San Jose, CA}{}{}{
  Company profiles, B2B. Data Engineering, Fuzzy search, Clustering
  % \newline{}%
  % Achievements:%
  \begin{itemize}%
    \item Increased search hit rate by 4\% by developing Spelling correction module. Applied Trie as BloomFilters, Count-min-sketch for language models. $7M$ unique words, $55M$ pairs, $55M$ triples.
    \item Researched and developed a de-duplication method for $600M$ company profiles. Locality sensitive hashing, MinHash, Trie as BloomFilters for Hamming distance. Found 7M exact and fuzzy duplicates.
    \item Implemented Verification and Identification services that match web domains to companies. $60M$ websites scale. 
  \end{itemize}
  Technologies: Scala, Python, Postgres, ML, AWS
}
\cventry{07.2014--01.2020}{Software Engineer}{Piano Media, Izhevsk, Russia}{}{}{
  AdTech, Platform for paywall and subscription business.
  Distributed systems, ML, Reports, DSL, Streaming. \\
  200 Tb data in total, $5000\, rps_{avg}$, $8000\, rps_{peak}$ daily.
  \begin{itemize}%
    \item Launched Likely-to-Subscribe and Likely-to-Churn ML projects, $10 M$ users
    \item Led and built a project that provides various types of analytic reports, real-time, on-demand, customizable reports based on DSL. Connected Clojure-based DSL with Spark and BigQuery.
    \item Implemented User Segmentation Engine, $100 M$ users, used Bloom filter as KV-store
  \end{itemize}
  Technologies: Scala, Clojure, Unix, Spark, HDFS, DSL, AWS, Akka, Kafka, Catboost, BigQuery
}
\cventry{08.2013--07.2014}{Researcher, Algorithm Engineer}{Huawei Research, Moscow, Russia}{}{}{
  RnD, Nested data parallelism model, distributed systems, map-reduce, optimization compiler, meta-programming and code generation, domain specific languages
  \begin{itemize}%
    \item Implemented Spark backend for nested data-parallelism model
    \item Researched and developed efficient custom Spark RDD's for NDP-primitives
  \end{itemize}
  Technologies: Scala, Spark, Distributed Programming, C++
}
\cventry{12.2007--08.2013}{Software Engineer}{Rosneft, Izhevsk, Russia}{}{}{
  Oil mining, forecast, and monitoring system. OLAP, up to $2 M$ data points per document, up to 15 dimensions, DSL, Calculations
  \begin{itemize}%
    \item Increased calculation speed by 3.5 times using multithreading evaluations
    \item Pioneered testing and verification via \href{https://en.wikipedia.org/wiki/Partial\_evaluation}{Partial evaluation}
  \end{itemize}
  Technologies: C\#, Multithreading, DSL, \href{https://en.wikipedia.org/wiki/Partial\_evaluation}{Partial evaluations}
}


\section{ACM ICPC}
\cvcomputer{coach}{2012, World Final, Poland, Warsaw}{participant}{2005, 2006, NEERC}

\section{Schools and conferences}
\cvline{DSLDI 2015}{\small Summer School on DSL Design and Implementation, Aug 2015, Lausanne, Switzerland}
\cvline{EWSCS 2014}{\small Estonian Winter School in Computer Science, Mar 2014, Palmse, Estonia}
\cvline{ALMADA~2013}{\small School on Algorithms for Massive Data, Aug 2013, Moscow, Russia}
\cvline{Russir 2011}{\small Russian Summer School in Information Retrieval, Aug 2011, Saint Petersburg, Russia}
\cvline{SSSEV 2011}{\small Summer School in Software Engineering and Verification, Jul 2011, Moscow, Russia}
\cvline{Russir 2010}{\small Russian Summer School in Information Retrieval, Sep 2010, Voronezh, Russia}
\cvline{conferences}{\href{http://www.highload.ru/}{HighLoad++-2014/2015/2019}, \href{http://meta2016.pereslavl.ru}{META-2014/2016}, \href{http://2013.nscf.ru/}{NSKF-2013/2014}, \href{http://2014.ulcamp.ru/}{ULMCAMP-2014}, \href{http://scalar-conf.com/}{Scalar-2017/2018/2019}, \href{https://nastachku.ru/}{STACHKA-2017}, \href{http://www.lambda.world/}{LambdaWorld-2017}, \href{https://fby.by/}{f(by)-2017/2019/2020}, \href{https://www.fpure.events/}{fpure-2019}, \href{https://pybay.com/}{PyBay-2022/2023}, \href{https://events.linuxfoundation.org/pytorch-conference/}{PyTorch-2023}, \href{https://current.confluent.io/}{Current-2024}, \href{https://raysummit.anyscale.com/}{Ray-2024}, \href{https://datastreaming-summit.org/event/north-america-2024}{DataStreaming-2024} \href{https://www.lambdaconf.us/}{LambdaConf-2025} }
\section{Main publications}
\cvline{}{\href{https://elar.urfu.ru/bitstream/10995/3710/3/RuSSIR\_2011_04.pdf}{D. V. Urbanovich, P. G. Ajtkulov, ''Simple algorithm to maintain dynamic suffix array for text indexes'', RuSSIR/EBDT, (2011), 40-45.}}
\cvline{}{\href{https://www.mathnet.ru/links/5def79b9da88e3a1755ed8f497457245/ubs377.pdf}{P. G. Ajtkulov, ''Symbol array processing'', UBS, 28 (2010), 126-178. (rus)}}
\section{Talks}
\cvline{HighLoad-2019}{Probabilistic data structures, \href{https://www.youtube.com/watch?v=Vx-l7KiIYuM&t}{https://www.youtube.com/watch?v=Vx-l7KiIYuM}, \href{https://www.highload.ru/moscow/2019/abstracts/5944}{https://www.highload.ru/moscow/2019/abstracts/5944}}
\cvline{EWSCS 2014}{19th Estonian Winter School in Computer Science, \href{http://cs.ioc.ee/ewscs/2014/index.php?page=../talks}{http://cs.ioc.ee/ewscs/2014/index.php?page=../talks} Online Suffix Array Construction}

\section{Collaboration}
\cvline{Dissernet}{\href{https://www.dissernet.org/}{https://www.dissernet.org/} Plagiarism detection in Ph.D. theses and articles in Russia. Algorithms on strings, text, table data analysis, and translation cases. ML/NLP, 1.2M theses and 90M articles, 3.5 Tb raw texts. Extra 2000 stolen dissertations and more than 40, 000 articles were founded.}
\cvline{Investigative journalism}{Various projects, record linkage, entity resolution, text classification on scale 12B messages, graph databases, graph analysis, data curation. ML/NLP, Clickhouse, Python, Scala, Elastic} 

\section{Misc}
\cvline{Translator}{\small Foundations for Programming Languages, John C. Mitchell. RCD press, 2010}
\cvline{Running}{Marathon: \href{https://www.athlinks.com/event/3241/results/Event/1036173/Course/2307831/Bib/5668}{3h22m}, $\frac{1}{2}$ marathon: 1h37m, 10km: 40m38s}
\cvline{Chess}{Max Elo: 2118}


\end{document}
